Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-11-04 reports/paper.tex
resolve issues regarding byline endnotes

\documentclass[amsmath,amssymb,twocolumn]{revtex4-1}

@@

\author{A.~R.~McCluskey}
\email{a.r.mccluskey@bath.ac.uk}
  \thanks{These authors have contributed equally to the work presented within}
  \altaffiliation[Also at ]{Diamond Light Source, Harwell Campus, Didcot,
  OX11 0DE, UK}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}

\author{A.~Sanchez-Fernandez}
  \thanks{These authors have contributed equally to the work presented within}
  \altaffiliation[Also at ]{European Spallation Source, SE-211 00 Lund,
  Sweden}
  \altaffiliation[Present address ]{Department of Food Technology, Lund
  University, SE-211 00 Lund, Sweden}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}

@@

\author{A.~J.~Jackson}
  \altaffiliation[Also at ]{Department of Physical Chemistry,
  Lund University, SE-211 00 Lund, Sweden}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

\author{R.~A.~Campbell}
  \altaffiliation[Also at ]{Institut Laue-Langevin, 71 avenue des Martyrs,
  38000, Grenoble, France}
\affiliation{Division of Pharmacy and Optometry, University of Manchester,
Manchester, UK}

\author{T.~Arnold}
\email{tom.arnold@esss.se}
  \altaffiliation[Also at ]{ISIS Neutron and Muon Source, Science and
  Technology Facilities Council, Rutherford Appleton Laboratory, Harwell
  Oxford, Didcot OX11 OQX, UK; Diamond Light Source, Harwell Campus, Didcot,
  OX11 0DE, UK; Department of Chemistry, University of Bath, Claverton Down,
  Bath, BA2 7AY, UK}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

@@

\begin{abstract}
  In this work, we present the first example of the self-assembly of
  phospholipid monolayers at the interface between air and a non-aqueous
  liquid.
  Deep eutectic solvents are a novel class of environmentally friendly
  non-aqueous room temperature liquids with tunable properties, that have
  wide ranging potential applications and are capable of promoting the
  self-assembly of surfactant molecules.
  We use a chemically-consistent Bayesian modelling of X-ray and neutron
  reflectometry measurements to show that these monolayers broadly behave
  as they do on water.
  However, the ability of the deep eutectic solvent to interact with the
  phosphatidylglycerol lipid head, leads to an apparent increase in its
  volume compared to that observed in water.
  No such change was observed for the phosphocholine head, indicating that
  such interactions are head, and therefore solvent, specific.
  This has important implications for the potential uses of these solvents
  and for our understanding of how biomolecules behave in the absence of water.
\begin{description}
\item[Usage]
Electronic Supplementary Information (ESI) available: All analysis/plotting
scripts and figure files, allowing for a fully reproducible, and automated,
analysis workflow for the work presented is available at
\url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.1464836)
under a CC-BY 4.0 license.
Reduced experimental datasets are available at
\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
\end{description}
\end{abstract}

@@

%\tableofcontents

>>>>

\documentclass[amsmath,amssymb,twocolumn,superscriptaddress,prl]{revtex4-1}

@@

\author{A.~R.~McCluskey}
\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
\email{a.r.mccluskey@bath.ac.uk}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}

\author{A.~Sanchez-Fernandez}
\thanks{A.R.M. and A.S.-F. contributed equally to this work.}
\altaffiliation[Present address ]{Department of Food Technology, Lund
University, SE-211 00 Lund, Sweden.}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}

@@

\author{A.~J.~Jackson}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
\affiliation{Department of Physical Chemistry, Lund University, SE-211 00
Lund, Sweden}

\author{R.~A.~Campbell}
\affiliation{Division of Pharmacy and Optometry, University of Manchester,
Manchester, UK}
\affiliation{Institut Laue-Langevin, 71 avenue des Martyrs, 38000, Grenoble,
France}

\author{T.~Arnold}
\email{tom.arnold@esss.se}
\affiliation{European Spallation Source, SE-211 00 Lund, Sweden}
\affiliation{ISIS Neutron and Muon Source, Science and Technology Facilities
Council, Rutherford Appleton Laboratory, Harwell Oxford, Didcot, OX11 0QX,
UK}
\affiliation{Diamond Light Source, Harwell Campus, Didcot, OX11 0DE, UK}
\affiliation{Department of Chemistry, University of Bath, Claverton Down,
Bath, BA2 7AY, UK}

@@

\begin{abstract}
  In this work, we present the first example of the self-assembly of
  phospholipid monolayers at the interface between air and a non-aqueous
  liquid.
  Deep eutectic solvents are a novel class of environmentally friendly
  non-aqueous room temperature liquids with tunable properties, that have
  wide ranging potential applications and are capable of promoting the
  self-assembly of surfactant molecules.
  We use a chemically-consistent Bayesian modelling of X-ray and neutron
  reflectometry measurements to show that these monolayers broadly behave
  as they do on water.
  However, the ability of the deep eutectic solvent to interact with the
  phosphatidylglycerol lipid head, leads to an apparent increase in its
  volume compared to that observed in water.
  No such change was observed for the phosphocholine head, indicating that
  such interactions are head, and therefore solvent, specific.
  This has important implications for the potential uses of these solvents
  and for our understanding of how biomolecules behave in the absence of water.
\end{abstract}

@@

%\tableofcontents
\begin{description}
\item[Usage]
Electronic Supplementary Information (ESI) available: All analysis/plotting
scripts and figure files, allowing for a fully reproducible, and automated,
analysis workflow for the work presented is available at
\url{https://github.com/arm61/lipids_at_airdes} (DOI: 10.5281/zenodo.1464836)
under a CC-BY 4.0 license.
Reduced experimental datasets are available at
\url{https://researchdata.bath.ac.uk/id/eprint/548}, under a CC-BY 4.0 license.
\end{description}
